%---------------------------------------------------------------------------------------------------
%		main.tex
%
%	This is the main file of the chapter that talk about the measurments.
%
%	Author: Andrea Meneghinello
% Version: 0.1
%	Table of changes:
%		21/03/2016 -> document definition
%---------------------------------------------------------------------------------------------------
\chapter{Comparative evaluation}
\label{cap:measurements}
As we argued in Chapter \ref{cap:elasticity} good elasticity mechanisms are needed to build a multi-tenant
software deployed in the cloud. These mechanisms, most of times, are based on threshold
evaluation (reactive mechanism) which move the work environments to a more powerful server in order
to support the current workload when the latter increases.

Our purpose is to prove that the Docker technology is able to better exploit the underlying hardware
capabilities, thus reducing the necessary relocations. We focused our attention on three axes: \acs{cpu},
storage and network.

By analysing the \acs{cpu} capacity we have tested how both environments are able to scale-in/scale-out
when they have to share computing resources with other intensive compute activities. Thus, we have proved
their adaptability, which is one of the requirements to gain elasticity (see Section 
\ref{sec:elasticity-requirements-adaptability}).

Instead, analysing the sustainable memory bandwidth we wanted to prove how containerization and virtualization
are able to exploit the available memory bandwidth; a good exploitation would reduce considerably the
number of scale-in/scale-out operations (i.e. scalability requirement described in Section 
\ref{sec:elasticity-requirements-scalability}). This would improve the scalability performance because
our service resides for a lot of time over the same machine (with more available memory or less active
users), before scaling to a better one, thus users do not wait for trade-off times.

Finally, through analysing network capabilities (bandwidth and latency) of both containerization and
virtualization technologies, we are able to know how the general performance increases or decreases
following a scale operation. Actually, composability (see Section 
\ref{sec:elasticity-requirements-composability}) is a requirement for elasticity as well as \ac{sla} 
awareness (see Section \ref{sec:elasticity-requirements-slaAwareness}). Measuring network bandwidth
and latency give us an idea about what \ac{sla} have to take into account to assure good \ac{qos}.

The fact that Linux is able to host both \ac{vm}s and Docker containers creates the opportunity for
an apple-to-apple comparison between these two virtualization technologies. Thus, in the following 
sections we report the results collected during the comparison tests. Each section illustrates the
purpose of the test, the collected results and tries to explain them.

\input{chapters/measurements/sections/introduction.tex}

\input{chapters/measurements/sections/cpu.tex}

\input{chapters/measurements/sections/storage.tex}

\input{chapters/measurements/sections/network.tex}

\input{chapters/measurements/sections/summary.tex}