%---------------------------------------------------------------------------------------------------
%		thanks.tex
%
%	This is the main file of the chapter that talk about the problem space.
%
%	Author: Andrea Meneghinello
% Version: 0.1
%	Table of changes:
%		15/03/2016 -> document definition
%---------------------------------------------------------------------------------------------------
\chapter*{Acknowledgements}
I would like to remind all those who have helped me in writing the thesis with suggestions, criticisms
and comments: to them goes all my gratitude, even if I'm the only responsible for any error contained
in this thesis.

I want to start by thanking prof. Tullio Vardanega for watching and supporting me during the last year
both as regard my last exams and for the final thesis. He gave to me the opportunity to understand,
through various reflections, how I really want to spend my cultural background.

I continue my thanks by citing Luca Righi to hosted and supported me the acoustic noise during the
execution of the practical tests. He was a valid support that introduced me in the world of Linux
server management.

A special thank you to all my colleagues and friends that encouraged me during the past two years,
for the beautiful moments spent together both in and out Torre Archimede (our second home).

And, last but not least I want to say a BIG THANK YOU to my parents Lauro, Franca, my sister Lisa
for giving me the opportunity to pursue my passion and complete my education that will be a solid
rock for the rest of my life, and another SPECIAL THANK YOU to my girlfriend Silvia for supporting all
my complaints and for giving me a great help with my academic career.